Project1_RM_Objective_1

### 2020-02-16 WorkingCode/Project1_RM_Objective_1.Rmd
Add files via upload

---
title:  "Project1_RM_Objective_1"
Author: "Reagan Meagher"
Date:   "2/10/2020"
---

@@

```{r create 90/10 train/test splits for each data source}
#Really handy predict function
predict.regsubsets =function (object , newdata ,id ,...){
  form=as.formula (object$call [[2]])
  mat=model.matrix(form ,newdata )
  coefi=coef(object ,id=id)
  xvars=names(coefi)
  mat[,xvars]%*%coefi
}
```

@@

INTUITIVE LINEAR - LINEAR
```{r intuitive model building}
#LINEAR - LINEAR
linear.intuitive.train.model <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = linear.train)
linear.intuitive.predictions <- linear.intuitive.train.model %>% predict(linear.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(linear.intuitive.predictions, linear.test$price))
print("Test Root Mean Square Error: ")
print(RMSE(linear.intuitive.predictions, linear.test$price))
print("Test Mean Absolute Error: ")
print(MAE(linear.intuitive.predictions, linear.test$price))
print("Prediction Error Rate: ")
RMSE(linear.intuitive.predictions, linear.test$price)/mean(linear.test$price)

@@

INTUITIVE LOG - LINEAR
```{r intuitive model building}
#LOG - LINEAR
log.intuitive.test.model <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = log.train)
log.intuitive.predictions <- log.intuitive.test.model %>% predict(log.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(log.intuitive.predictions, log.test$lprice))
print("Test Root Mean Square Error: ")
print(RMSE(log.intuitive.predictions, log.test$lprice))
print("Test Mean Absolute Error: ")
print(MAE(log.intuitive.predictions, log.test$lprice))
print("Prediction Error Rate: ")
RMSE(log.intuitive.predictions, log.test$lprice)/mean(log.test$lprice)

@@

FORWARD LINEAR
```{r forward selection model}
#FORWARD LINEAR
set.seed(77)

@@

FORWARD LOG
```{r forward selection model}
#FORWARD LOG
set.seed(77)

@@

BACKWARD LINEAR
```{r backward selection model}
set.seed(77)

@@

BACKWARD LOG
```{r backward selection model}
set.seed(77)

@@

SEQREP LINEAR
```{r seqrep selection model}
set.seed(77)

@@

seqrep LOG
```{r seqrep selection model}
set.seed(77)

>>>>

---
title: "Project1_RM_Objective_1"
Date: 2/10/2020
Author: Reagan Meagher
---

@@

```{r hold predict function}
#Really handy predict function
predict.regsubsets =function (object , newdata ,id ,...){
  form=as.formula (object$call [[2]])
  mat=model.matrix(form ,newdata )
  coefi=coef(object ,id=id)
  xvars=names(coefi)
  mat[,xvars]%*%coefi
}
```

@@

INTUITIVE LINEAR - LINEAR
```{r intuitive model building - linear}
#LINEAR - LINEAR
linear.intuitive.train.model <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = linear.train)
linear.intuitive.predictions <- linear.intuitive.train.model %>% predict(linear.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(linear.intuitive.predictions, linear.test$price))
print("Test Root Mean Square Error: ")
print(RMSE(linear.intuitive.predictions, linear.test$price))
print("Test Mean Absolute Error: ")
print(MAE(linear.intuitive.predictions, linear.test$price))
print("Prediction Error Rate: ")
RMSE(linear.intuitive.predictions, linear.test$price)/mean(linear.test$price)

@@

INTUITIVE LOG - LINEAR
```{r intuitive model building - log}
#LOG - LINEAR
log.intuitive.test.model <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = log.train)
log.intuitive.predictions <- log.intuitive.test.model %>% predict(log.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(log.intuitive.predictions, log.test$lprice))
print("Test Root Mean Square Error: ")
print(RMSE(log.intuitive.predictions, log.test$lprice))
print("Test Mean Absolute Error: ")
print(MAE(log.intuitive.predictions, log.test$lprice))
print("Prediction Error Rate: ")
RMSE(log.intuitive.predictions, log.test$lprice)/mean(log.test$lprice)

@@

FORWARD LINEAR
```{r forward selection model - linear}
#FORWARD LINEAR
set.seed(77)

@@

FORWARD LOG
```{r forward selection model - log}
#FORWARD LOG
set.seed(77)

@@

BACKWARD LINEAR
```{r backward selection model - linear}
set.seed(77)

@@

BACKWARD LOG
```{r backward selection model - log}
set.seed(77)

@@

SEQREP LINEAR
```{r seqrep selection model - linear}
set.seed(77)

@@

seqrep LOG
```{r seqrep selection model - log}
set.seed(77)
